### 2023-06-14 resilience-safe-down.tex
up

\mathieu{Remarquer que les résultats sont aussi valide si on n'a pas safe et bad complémentaires mais juste $\Bad=\uparrow \Bad$ and $\Safe=\downarrow \Safe$}

>>>>

Remark we did not make use of the hypothesis $\Bad$ complement of $\Safe$, simply 
$\Bad=\uparrow \Bad$ and $\Safe=\downarrow \Safe$, thus 
the above results still hold in the more general case where $\Bad$ and $\Safe$ are not complement of each others.

### 2023-06-14 resilience.tex
up

While considering a sequence of configurations, every prefix is always 
either in the case that the latest visited $\Bad$ configuration has already been followed by a $\Safe$ configuration
or in the case that it still has to. 
Thus, in context, there are no true ``neutral'' configurations: either a neutral configuration is contextually ``$\Safe$'' because it follows a visit in a $\Safe$ configuration, either it is contextually ``$\Bad$'' because it follows a visit in a $\Bad$ configuration and has, accordingly, to reach a $\Safe$ one.
Hence we will consider not only $\Bad$ and $\Safe$ disjoint but
% w.l.o.g.
	also
$\Bad$ complement of $\Safe$,
in which case
if $\Bad$ is downward-closed then $\Safe$ is upward-closed and vice-versa.
Cases where $\Bad$ or $\Safe$ are not complements of each other, and share closure properties, i.e. are both downward-closed or both upward-closed,
have also been studied, 
see 
Appendix~\ref{case down down}
and
Appendix~\ref{case up up} for results.

\mathieu{Beaucoup plus dévellopper le paragraphe ci-dessus et expliciter qu'à partir de maintenant, on considère $\Bad$ complémentaire de $\Safe$ par défaut.}

>>>>

Given a set of states $S$, with two subsets $\Bad$ and $\Safe$, it is useful to note that in a sequence of states of $S$, every prefix is always 
either in the case that the latest visited $\Bad$ state has already been followed by a 
$\Safe$ state
or in the case that it still has to. 
Thus, \emph{in context}, there are no true ``neutral'' state: either a neutral state is contextually ``$\Safe$'' because it follows a visit in a $\Safe$ state, either it is contextually ``$\Bad$'' because it follows a visit in a $\Bad$ state and has, accordingly, to reach a $\Safe$ one.
Hence we will consider in the following not only that $\Bad$ and $\Safe$ are disjoint but
% w.l.o.g.
	also
that $\Bad$ is the complement of $\Safe$,
in which case
if $\Bad$ is downward-closed then $\Safe$ is upward-closed and vice-versa.
Cases where $\Bad$ or $\Safe$ are not complements of each other, and share closure properties, i.e. are both downward-closed or both upward-closed,
have also been studied, 
see 
Appendix~\ref{case down down}
and
Appendix~\ref{case up up} for results.
